What is disputed on the web?

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Improved statement filtering and allowed it to be done in the same pass as noun extraction

We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.

@@

We form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g. '.','?','!',\texttt{</p>},\texttt{</h1>}, etc).

We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages. The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range. We thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

>>>>

We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
{\bf either put here the other related work on this, or just put this reference in the related work section-- especially because there much more important work beyond hearst92, so no need to give it much emphasis in the intro}

@@

We form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g. '.','?','!',\texttt{</p>},\texttt{</h1>}, etc). 
{\bf it would be quite important to give a sense on the accuracy --precision - of the claims extracted. you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}

{\bf is it really important the discussion on the date and search technique? i think it deviates from the main points and is kind of long}
We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages. The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range. We thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

\x{Talk about how we plan to have a much bigger data set in the future. This is just the start.}
